---
title       : course project
subtitle    : predict car's fuel efficiency 
author      : Land
job         : please use right or left arrow key to nevigate these slides.
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Predictive the fuel efficiency of your car

* Fuel efficiency is one of features that we consider when we buying a car.

* Here, we define the fuel efficiency as “Miles/ gallon”.

* we develop the predicting model by use the data "mtcars"

```{r}
head(mtcars)
```

--- .class #id 

## Building Linear Regression Model

* We choose 2 features, type of transmission and 1/4 mile time as predictors.

* The “Miles/ gallon” is our outcome. 

* Use simple linear regression

* R code:
```{r, cache=TRUE, results='hide'}
fit2 <- lm(mpg ~ factor(am) + qsec, mtcars)
```

---

## Result

```{r, cache=TRUE, echo=FALSE, results='hide'}
data(mtcars)
fit2 <- lm(mpg ~ factor(am) + qsec, mtcars)
```

```{r, cache=TRUE}
summary(fit2)$coefficients
```

So our prediction model will be:

* If the transmission of the car is automatic:
-18.88 + 1.98 * 1/4 mile time

* If the trans mission of the car is manual:
-18.88 + 8.87 + 1.98 * 1/4 mile time  

*you can find the app here:
[https://land.shinyapps.io/car-app/](https://land.shinyapps.io/car-app/)

---
## Reference

Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.


